Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-10-23 manuscript.Rmd
cite HARKing properly
Update manuscript.Rmd

1. We know with absolute certainty that reported results came about by p-hacking.
2. The hypothesis was picked to explain the results.
3. We cannot exclude the possibility of p-hacking having led to the reported results.
4. Reported results were obtained by planned exploration.
5. Reported results were obtained by unplanned exploration.

@@

Our emphasis on transparency aligns with other justifications of preregistration, especially those put forth by @lakensValuePreregistrationPsychological2019's, although based on quite different philosophical foundations.
Our goal is to contribute a rationale that more comprehensively captures the spectrum of exploration and confirmation in relation to preregistrations, post-hoc changes of preregistrations, and subjective evaluations of evidence.
We find it difficult to content ourselves with vague terms like "control" or "transparency" if they ultimately remain unconnected to how much researchers believe in a theory.
In our framework, researchers can input what they assume other researchers think and calculate what their actions, be it the preregistration itself or later deviations, may have on their readers.
We put subjective evaluations at the centre of our consideration; we deal explicitly with researchers who are proponents of some theory (they have higher priors for the theory being true), researchers who suspect confounding variables (they assume lower theoretical risk), or those who remain doubtful if everything relevant was reported (they have higher uncertainty about theoretical risk) or even those who place greater value on incongruent evidence then others (they differ in their confirmation function).
We, therefore, hope to not only provide a rationale for preregistration for those who subscribe to a Bayesian philosophy of science but also a framework to navigate the complicated questions that arise in the practice of preregistration.

>>>>

1. We know with absolute certainty that reported results came about by p-hacking.
2. A hypothesis was picked to explain reported results after the fact [HARKing, @kerrHARKingHypothesizingResults1998].
3. We cannot exclude the possibility of p-hacking having led to the reported results.
4. Reported results were obtained by planned exploration.
5. Reported results were obtained by unplanned exploration.

@@

Our emphasis on transparency aligns with other justifications of preregistration, especially those put forth by @lakensValuePreregistrationPsychological2019's, although based on quite different philosophical foundations.
Our goal is to contribute a rationale that more comprehensively captures the spectrum of exploration and confirmation in relation to preregistrations, post-hoc changes of preregistrations, and subjective evaluations of evidence.
We find it difficult to content ourselves with vague terms like "control" or "transparency" if they ultimately remain unconnected to how much researchers believe in a theory.
Within our framework, researchers have the ability to input their assumptions regarding the perspectives of other researchers and calculate the potential impact of their actions on their readership, whether these actions relate to study design, to the preregistration itself, or subsequent deviations from it.
We put subjective evaluations at the centre of our consideration; we deal explicitly with researchers who are proponents of some theory (they have higher priors for the theory being true), researchers who suspect confounding variables (they assume lower theoretical risk), or those who remain doubtful if everything relevant was reported (they have higher uncertainty about theoretical risk) or even those who place greater value on incongruent evidence then others (they differ in their confirmation function).
We, therefore, hope to not only provide a rationale for preregistration for those who subscribe to a Bayesian philosophy of science but also a framework to navigate the complicated questions that arise in the practice of preregistration.
